Silver Ion Chroma

### 2020-12-14 silver_ion_chroma.Rmd
fixed facet wrap

---
title: "Silver Ion Chroma"
author: "Tristan Caro"
date: "12/10/2020"
output:
  html_document:
    toc: true
    toc_float: true
---

@@

## Plot
```{r, echo = FALSE, warning=FALSE}
p_tc_bames2 <- results %>%
  filter(sample == c("tc_bames2")) %>% 
  ggplot() +
  aes(`Retention Time`, `Relative Height`, fill = `Peak Name`) +
  geom_bar(stat = 'identity', width = 0.1)+
  scale_fill_viridis_d() +
  ggtitle("BAMES Standard 10µg/µL") +
  theme_bw()

@@

### Issue with R plotting
Facet wrapping results in incomplete plotting - data points in tc_bames2 are not plotted.
```{r}
p_tc_bames2 <- results %>%
  filter(sample == c("tc_bames2", "bames_disc_f1", "bames_nitr_f1")) %>% 
  ggplot() +
  aes(`Retention Time`, `Relative Height`, fill = `Peak Name`) +
  geom_bar(stat = 'identity', width = 0.1)+
  facet_wrap(~sample, nrow = 1, scales = "free_y") +
  scale_fill_viridis_d() +
  ggtitle("BAMES Standard 10µg/µL") +
  theme_bw()

>>>>

---
title: "Silver Ion Chroma"
author: "Tristan Caro"
date: "12/10/2020"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 3
---

@@

#Plots
Plots generated using `ggplot2` and `plotly`.

## Overview Plot
```{r, echo = FALSE, warning=FALSE}
factored_samples <- c('tc_bames2','bames_disc_f1','bames_disc_f2','bames_disc_f3', 'bames_nitr_f1', 'bames_nitr_f2', 'bames_nitr_f3')
results$sample_f = factor(results$sample, levels=factored_samples)

plot_results <- results %>% 
  filter(sample %in% c('tc_bames2', 'bames_disc_f1', 'bames_disc_f3', 'bames_nitr_f1'))

p_tc_bames2 <- plot_results %>%
  ggplot() +
  aes(`Retention Time`, `Relative Height`, fill = `Peak Name`) +
  geom_bar(stat = 'identity', width = 0.1)+
  facet_wrap(~sample_f, ncol = 1, scales = "free_y") +
  scale_fill_viridis_d() +
  ggtitle("BAMES Standard 10µg/µL") +
  theme_bw()

## Individual Plots

```{r, echo = FALSE, warning=FALSE}
p_tc_bames2 <- results %>%
  filter(sample == c("tc_bames2")) %>% 
  ggplot() +
  aes(`Retention Time`, `Relative Height`, fill = `Peak Name`) +
  geom_bar(stat = 'identity', width = 0.1)+
  scale_fill_viridis_d() +
  ggtitle("BAMES Standard 10µg/µL") +
  theme_bw()

@@
